Relationships in the extremes and their influence on competition and coexistence

### 2022-04-21 paper/Paper.Rnw
added paragraph on ATA specialists

%ATA specialists
Contributions of ATAs to species coexistence open the possibility that
``ATA specialists'' may exist in some contexts. If a stronger competitor is present across a
landscape and the GWR of a weaker competitor %***DAN: Dan is working right here.

%Not only is the contribution of ATA non-neglible but in some cases the presence or absence of ATAs 
%can mediate the result of competition between species, i.e., coexistence or extirpation. 
%For some parameters, the contribution of ATAs was the driving mechanism of 
%coexistence -- GWR would be negative without it -- deeming the scenario a case of 
%ATA rescue. For other parameter values, ATA exclusion occurs where ATAs are the 
%driving mechanism of the failure to coexist (exclusion) and the lack of ATAs would result in 
%a positive GWR. Parameter
subspaces of ATA exclusion and ATA rescue suggest a new kind of specialization among species or \emph{ATA specialists} - species which only persist in habitat patches where ATAs contribute to its coexistence. 
One can imagine a species whose coexistence with others is conditional on the asymmetric relationship between drivers of coexistence and whose populations may become excluded when ATAs erode. 
%I think ata specialists are a thing - if their competitor is ubiquitous, they can only live in places on the landscape 
%where there are atas. Could have a discussion para on it, if it does not make the results. Or both. BTW, ATA exclusion has a 
%similar thing going on - a species excluded by ATAs (and competition) can only live on the portions of the landscape where
%there are no ATAs. Could also describe the temporal way of it - the ATA specialist can only survive in a era/epoch for which there
%are ATAs in its local, otherwise it'll have to go dormant or move elsewhere.

>>>>

%ATA specialists
Contributions of ATAs to species coexistence open the possibility that
``ATA specialists'' may exist in some contexts. If a strong competitor is present across a
network of habitat patches and the GWR of a weaker competitor is only positive 
in a patch in the presence of 
ATAs between the temporal fluctuations of two environmental variables in that patch,
then the weaker competitor can only persist in patches for which ATAs are present,
and can therefore be regarded as an ``ATA specialist'' in the landscape. EC-associations
can often boil down to associations between two environmental variables, as was the case
for the lottery model we considered. Mechanisms of coexitence should correspond to
means by which niche differentiation is possible. Thinking about our new mechanism of 
coexistence in terms of possible ATA specialists helps highlight this connection. Likewise,
because we have described ATA exclusion as well as ATA rescue, it is possible to 
imagine a scenario in which a weaker competitor can only exist in habitat patches 
for which ATAs are absent, and is hence a specialist on scenarios with symmetric
tail associations of environmental variables (an ``STA-specialist''). Additional 
research will be needed to assess to what degree these possibilities are realized 
in nature.
